### 2020-02-03 nlp_models.tex
updating nlp

also differs significantly between GPT and GPT2.
Figure \ref{fig:gpt-alpha-layer} plots $\alpha$ vs the depth (i.e. a layer id) for each model.
The deficient GPT model displays two trends in $\alpha$ , one stable with $\alpha\sim 4$,
and one increasing with layer id, with $\alpha$ reaching as high as $12$.
In contrast, the well-trained GPT2 model shows consistant and stable patterns, again
with one stable $\alpha\sim 3.5$ (and below the GPT trend), and the other only
slightly trending up, with $alpha\le 6$. 
Again, the scale-invariant $\alpha$ metric lets us identify potentially
poorly-trained models.

Notice also that the Spectral Norms
(Figure \ref{fig:gpt-snorm-layer})
and the $\alpha-$Norms
(Figure \ref{fig:gpt-pnorm-layer})
display an unusually some mall values for GPT,
and some increasing trending values for GPT2.
Generally speaking, we do not think scale-dependennt 
norm metrics can be directly applied to distinguish ``good'' vs ``bad''  models 
because of the anamalous scale collapse that is observed in bad models.

\charles{Discuss Spectral Norm, alpha-Norm}

>>>>

also differs significantly between GPT and GPT2.
Figure \ref{fig:gpt-alpha-layer} plots $\alpha$ vs the depth (i.e. a layer id) for each model.
The deficient GPT model displays two trends in $\alpha$ , one stable with $\alpha\sim 4$,
and one increasing with layer id, with $\alpha$ reaching as high as $12$.
In contrast, the well-trained GPT2 model shows consistant and stable patterns, again
with one stable $\alpha\sim 3.5$ (and below the GPT trend), and the other only
slightly trending up, with $alpha\le 6$. 
The scale-invariant $\alpha$ metric lets us identify potentially
poorly-trained models.

Notice also that the Spectral Norms
(Figure \ref{fig:gpt-snorm-layer})
and the $\alpha-$Norms
(Figure \ref{fig:gpt-pnorm-layer})
display an unusually some mall values for GPT,
and some increasing trending values for GPT2.
Generally speaking, we do not think scale-dependennt 
norm metrics can be directly applied to distinguish ``good'' vs ``bad'' models 
because of the anamalous scale collapse that is frequently observed in bad models.
